\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

%\renewcommand{\baselinestretch}{2}

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document
\pdfminorversion=4
\input{macros}

\title{\LARGE \bf Distributed Synthesis of Surveillance Strategies for Mobile Sensors}

\author{Suda Bharadwaj$^{1}$ and Rayna Dimitrova$^{2}$ and Ufuk Topcu$^{1}$% <-this % stops a space
%\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$Suda Bharadwaj and Ufuk Topcu are with the University of Texas at Austin}%
\thanks{$^{2}$Rayna Dimitrova is with the University of Leicester, UK.}%
}



\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
We study the problem of synthesizing strategies for a mobile sensor network to conduct surveillance in partnership with static alarm triggers. We formulate the problem as a multi-agent reactive synthesis problem with surveillance objectives specified as a temporal logic formula. In order to avoid the state space blow-up arising from a centralized strategy computation, we propose a method to \emph{decentralize} the surveillance strategy synthesis by decomposing the multi-agent game into subgames that can be solved independently. We also decompose the global surveillance specification into local specifications for each sensor and show that sensors satisfying their local surveillance specifications guarantees the sensor network as a whole will satisfy the global surveillance objective. Thus, our method is able to guarantee global surveillance properties in a mobile sensor network while synthesizing completely decentralized strategies with no need for communication between the sensors. We also present a case study where we demonstrate an application of decentralized surveillance strategy synthesis.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{INTRODUCTION}
\input{introduction.tex}

\section{MOTIVATING CASE STUDY}\label{sec:casestudy}
\input{casestudy.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{GAMES WITH SURVEILLANCE OBJECTIVES}
\input{games.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{DISTRIBUTED SURVEILLANCE GAMES}
\input{distgames.tex}

\section{FROM GLOBAL TO LOCAL SPECIFICATIONS}
\input{specs.tex}
%
%\section{DECENTRALIZED SYNTHESIS}
%\input{synthesis.tex}

\section{EXPERIMENTAL EVALUATION}\label{sec:experiments}
\input{experiments.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{CONCLUSIONS}
We presented a method for decentralized synthesis of surveillance strategies for a mobile sensor network working with static sensors. Problems that would otherwise be computationally intractable can be solved by decomposing the global game into local subgames for each sensor with individual surveillance specifications. We show that though each game is solved completely independently with no information sharing, we can still guarantee global surveillance properties.

For future work, we aim to incorporate false positives in static alarm triggers as well as noisy observations from the mobile sensors while still guaranteeing surveillance specifications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section*{APPENDIX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section*{ACKNOWLEDGMENT}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{IEEEtran}
\bibliography{main}

\end{document}
